---
title: 'Assignment #3'
author: "Kyle Pinca"
date: "10/27/2021"
output: html_document

## Question 1
```{r}
Bank = read.csv("bank marketing.csv")
str(Bank)
Bank$y=as.factor(Bank$y)
class(Bank$y)
attach(Bank)
```

## Question 2 
```{r}
set.seed(10)
train=sample(nrow(Bank),nrow(Bank)/2)

```

## Question 3
```{r}
bank.fit=glm(y~. -duration, data=Bank, subset=train, family=binomial)
summary(bank.fit)
```
"There seems to be alot of predictors that are not statsically signficant, based on their p-value"

## Question 4
```{r}

bank.prob=predict(bank.fit, newdata=Bank[-train,], type="response")
```

## Question 5
```{r}
bank.pred=ifelse(bank.prob>0.5,"Yes","No")
```
## Question 6
```{r}
table(bank.pred, y[-train])
```

## Question 7
  # Overall Error Rate:
```{r}

sum(bank.pred!=y[-train])/length(y[-train])
```
  # Type I error:
```{r}
sum((bank.pred=="Yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```
  # Type II error:
```{r}
sum((bank.pred=="No")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```

## Question 8
```{r}
bank.pred2=ifelse(bank.prob>0.1,"Yes","No")
table(bank.pred2,y[-train])
```
  # Overall Error Rate:
```{r}
sum(bank.pred2!=y[-train])/length(y[-train])
```
  # Type I Error:
```{r}
sum((bank.pred2=="Yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```
  # Type II Error:
```{r}
sum((bank.pred2=="No")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```

## Question 9
```{r}
bank.pred3=ifelse(bank.prob>0.05,"Yes","No")
table(bank.pred3,y[-train])
```

  # Overall Error Rate:
```{r}

```

  # Type I Error:
```{r}
sum((bank.pred3=="Yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```
  # Type II Error:
```{r}
sum((bank.pred3=="No")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```

## Question 10
  # ROC
library(ROCR)
```{r}
rocplot=function(pred, truth, ...){
  predob=prediction(pred, truth)
  perf=performance(predob, "tpr", "fpr")
  plot(perf,...)}

rocplot(bank.prob, y[-train], col="blue")
```
  
  #AUC
```{r}
auc=function(pred, truth){
  predob=prediction(pred, truth)
  perf=performance(predob, "auc")
  return(perf@y.values[[1]])}

auc(bank.prob, y[-train])
```

## Question 11
```{r}
"The model has high error rates due to how far the line is from 1 for true postive"
```

## Question 12
library(MASS)
```{r}
bank.lda=lda(y~.-duration, data= Bank,subset=train)
bank.lda.prob=predict(bank.lda, newdata=Bank[-train,], type="response")


bank.lda.pred=predict(bank.lda, Bank[-train,])
names(bank.lda.pred)

bank.pc=ifelse(bank.lda.pred$posterior[,2]>0.5,"Yes","No")
table(bank.pc, y[-train])
```
  # Overall
```{r}

```
  # Type I Error:
```{r}
sum((bank.pc=="Yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```

  #Type II Error:
```{r}
sum((bank.pc=="No")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```

## Question 13
```{r}
rocplot(bank.lda.pred$posterior[,2], y[-train], col="red")
legend(x=0.67, y=0.1,legend="LDA",col="red",lwd=1,bty="n")
auc.lda=auc(bank.lda.pred$posterior[,2], y[-train])
auc.lda
legend(x=0.85, y=0.1,legend=round(auc.lda,5),bty="n")
```

## Question 14
```{r}
bank.qda=qda(y~.-duration -loan -default, data= Bank,subset=train)
bank.qda

bank.qpred=predict(bank.qda, Bank[-train,])
bank.qpc=ifelse(bank.qpred$posterior[,2]>0.5,"Yes","No")
table(bank.qpc, y[-train])
```
  # Overall
```{r}

```
  # Type I Error:
```{r}
sum((bank.qpc=="Yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```
  # Type II Error:
```{r}
sum((bank.qpc=="No")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```

## Question 15
```{r}
rocplot(bank.qpred$posterior[,2], y[-train], col="red")
legend(x=0.67, y=0.1,legend="LDA",col="red",lwd=1,bty="n")
auc.lda=auc(bank.qpred$posterior[,2], y[-train])
auc.lda
legend(x=0.85, y=0.1,legend=round(auc.lda,5),bty="n")
```

## Question 16
library(e1071)
```{r}
bank.nb=naiveBayes(y~.-duration, data=Bank, subset=train)
bank.nb

bank.nb.class=predict(bank.nb, Bank[-train,])

table(bank.nb.class, y[-train])



```
  # Overall:
```{r}

```
  
  #Type I  Error
```{r}
sum((bank.nb.class=="yes")&(y[-train]=="no"))/sum(y[-train]=="no")
```
  
  #Type II Error
```{r}
sum((bank.nb.class=="no")&(y[-train]=="yes"))/sum(y[-train]=="yes")
```
  
  
  
## Question 17
```{r}
bank.nb.preds=predict(bank.nb, Bank[-train,], type="raw")

rocplot(bank.nb.preds[,2], y[-train], col="brown")
legend(x=0.67, y=0.31,legend="naiveB",col="brown",lwd=1,bty="n")
auc.nb=auc(bank.nb.preds[,2], y[-train])
auc.nb
legend(x=0.85, y=0.31,legend=round(auc.nb,5),bty="n")
```

## Question 18
```{r}
"It seems that logistic regression is best due to its higher auc"
```
